A greedy algorithm for the cardinality-constrained college application problem

### 2023-03-12 paper_alma/body.tex
correct calculation error in linear utility example

\begin{example} \label{tightexampleforconcavity}
For a small constant $\varepsilon \in (0, 1)$, define the market as follows.
\begin{center}
\begin{tabular}{r|cccccccc}
$j$   & $1$ & $2$ & $\cdots$ & $m-1$ & $m$ \\ \hline
$f_j$ & $\varepsilon^{1}$ & $\varepsilon^{2}$ & $\cdots$ & $\varepsilon^{m-1}$ & $\varepsilon^{m}$ \\
$t_j$ & $\varepsilon^{-1}$ & $\varepsilon^{-2}$ & $\cdots$ & $\varepsilon^{-(m-1)}$ & $\varepsilon^{-m}$
\end{tabular}%
\end{center}
The optimal portfolios are given by $\mathcal{X}_h = \{m-h + 1, \dots, m\}$, and 
% todo: correct the last equality here. Should be \approx with appropriate explanation.
% todo: upstream this change to the thesis text as well.
\begin{equation*}
v(\mathcal{X}_h) = \sum_{j= m-h +1}^m \Bigl( f_j t_j \prod_{i = j+1}^m (1 - f_{i}) \Bigr) =  \sum_{j= 1}^h  (1 - \varepsilon)^{j-1}.
\end{equation*}
Thus, as $\varepsilon$ approaches zero, we have $v(\mathcal{X}_h) \to h$.
\end{example}

>>>>

\begin{example} \label{tightexampleforconcavity}
For a small constant $\varepsilon \in (0, 1)$, define the market as follows.
\begin{center}
\begin{tabular}{r|cccccccc}
$j$   & $1$ & $2$ & $\cdots$ & $m-1$ & $m$ \\ \hline
$f_j$ & $\varepsilon^{1}$ & $\varepsilon^{2}$ & $\cdots$ & $\varepsilon^{m-1}$ & $\varepsilon^{m}$ \\
$t_j$ & $\varepsilon^{-1}$ & $\varepsilon^{-2}$ & $\cdots$ & $\varepsilon^{-(m-1)}$ & $\varepsilon^{-m}$
\end{tabular}%
\end{center}
The optimal portfolios are given by $\mathcal{X}_h = \{m-h + 1, \dots, m\}$, for which
\begin{equation*}
v(\mathcal{X}_h) =
\sum_{j = m-h +1}^m \left( f_j t_j \prod_{i = j+1}^m (1 - f_{i}) \right) =
\sum_{j = m-h +1}^m \left( \prod_{i = j+1}^m (1 - \varepsilon^i) \right).
\end{equation*}
This expression is bound from above by $\sum_{j = m-h +1}^m 1 = h$, and from below by
\[\sum_{j = m-h +1}^m \left( \prod_{i = j+1}^m (1 - \varepsilon) \right)
= \sum_{j = m-h +1}^m \left( \prod_{i = j+1}^m (1 - \varepsilon)^{m-j} \right)
\geq \sum_{j = m-h +1}^m (1 - \varepsilon)^m
= h (1 - \varepsilon)^m.\]
Thus, as $\varepsilon$ approaches zero, we have $v(\mathcal{X}_h) \to h$.
\end{example}
